---
title: "simpleRegress"
author: "Janette Quezada"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp2 <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp2)
summary.lm(simp2)
```


The adjusted R square is smaller 0.5321 for the headwdth than the neck model which is 0.7476

```{r}
simp3 <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp3)
summary.lm(simp3)
```



The adjusted R squared for the weight is 0.7423 it is smaller than the neck model which is 0.7476


```{r}
simp4 <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp4)
summary.lm(simp4)
```


The adjusted r square is higher than the neck model which  0.7476 the adjusted r square for the chest is 0.7869. 

```{r}
simp5 <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp5)
summary.lm(simp5)
```


The adjusted R square on HEADLEN is 0.8434 seems that the adjusted r square is getting bigger


```{r}
simp6 <- lm(LENGTH~as.numeric(SEX),data=bears)
plot(LENGTH~as.numeric(SEX),data=bears)
abline(simp6)
summary.lm(simp6)
```


The adjusted R square is too small to considered being that the number is -0.008373


```{r}
simp7 <- lm(LENGTH~as.numeric(MONTH),data=bears)
plot(LENGTH~as.numeric(MONTH),data=bears)
abline(simp7)
summary.lm(simp7)
```



The Rsquare variable is too small to consider in this model it is -0.01153.

```{r}
simp8 <- lm(LENGTH~as.numeric(AGE),data=bears)
plot(LENGTH~as.numeric(AGE),data=bears)
abline(simp8)
summary.lm(simp8)
```




The adjusted R square is better than month and sex but it is still a small number which is 0.5073 compared to the neck model number which is 0.7476 for neck


